Analysis

### 2023-03-20 Analysis.rmd
update figure code

@@

  component_plot <- function(df, scale_filter, type_filter) {
    df |>
      filter(scale == scale_filter) |>
      filter(target_type == type_filter) |>
      ggplot(aes(x = reorder(Model, (interval_score)), y = value, fill = Model, 
                 group = Model, alpha = `WIS components`)) + 
      scale_alpha_manual(values = c(1, 0.1, 0.6)) +
      # scale_fill_manual(values = vals) + 
      geom_bar(stat = "identity", position = "stack",
               color = "black",
               size = 0.1,
               width = 0.8) +
      facet_wrap(~ horizon, ncol = 4, 
                 strip.position = "bottom") + 
      theme_scoringutils() + 
      # theme(axis.text.x = element_blank()) + 
      theme(axis.text.x = element_blank(),
            axis.line.x = element_blank(), 
            axis.ticks.x = element_blank(),
            plot.title = element_text(hjust = 0.5,
                                      size = 8)) + 
      labs(x = NULL, y = "WIS", title = paste(type_filter, "-", scale_filter)) 
  }

@@

@@

@@

>>>>

avail |> 
  group_by(target_type, type) |>
  summarise(
    mean = mean(`Number forecasts`), 
    median = median(`Number forecasts`), 
    min = min(`Number forecasts`), 
    max = max(`Number forecasts`)
  )

@@

  component_plot <- function(df, scale_filter, type_filter) {
    df |>
      filter(scale == scale_filter) |>
      filter(target_type == type_filter) |>
      ggplot(aes(x = Model, 
                 # x = reorder(Model, (interval_score)), 
                 y = value, fill = Model, 
                 group = Model, alpha = `WIS components`)) + 
      scale_alpha_manual(values = c(1, 0.1, 0.6)) +
      # scale_fill_manual(values = vals) + 
      geom_bar(stat = "identity", position = "stack",
               color = "black",
               size = 0.1,
               width = 0.8) +
      facet_wrap(~ horizon, ncol = 4, 
                 strip.position = "bottom") + 
      theme_scoringutils() + 
      scale_y_continuous(label = label_fn) +
      # theme(axis.text.x = element_blank()) + 
      theme(axis.text.x = element_blank(),
            axis.line.x = element_blank(), 
            axis.ticks.x = element_blank(),
            plot.title = element_text(hjust = 0.5,
                                      size = 8)) + 
      labs(x = NULL, y = "WIS", title = paste(type_filter, "-", scale_filter)) 
  }

@@

scores$model |> unique()

@@

# Sinificance and bootstrap analysis

```{r}
scores |>
  filter(model %in% models_non_human) |>
  filter(horizon == 2) |>
  summarise_scores() |>
  select(model, forecast_date, type_and_scale, interval_score) |>
  pivot_wider(names_from = model, values_from = interval_score) |>
  group_by(type_and_scale) |>
  summarise(p1 = wilcox.test(`EuroCOVIDhub-ensemble`,`crowd-direct`, paired = TRUE)$p.value, 
            p2 = wilcox.test(`EuroCOVIDhub-ensemble`,`crowd-ensemble`, paired = TRUE)$p.value, 
            p3 = wilcox.test(`EuroCOVIDhub-ensemble`,`crowd-rt`, paired = TRUE)$p.value)

wilcox.test(1:20, 2:21) |> str()

@@

```{r}
epinow2_data |>
  score()
```
